---
title: "ConcGadget"
author: "Jason Parise"
date: "`r Sys.Date()`"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Concentration Calculations Gadget

In all biotechnology laboratories, frequent calculations for the concentrations
and volumes of dilutions of reagents are required. This can be a time
consuming task when many experiments are running. This concentration 
calculation gadget is a tool to hasten spur-of-the-moment calculations 
as scientists expedite their research.

The calculations conducted in this gadget utilize the fundamental principle
of the Dilution Equation: M1V1=M2V2.

## Concentration Calculation Gadget

```{r eruptions}
library(shiny)
library(miniUI)

shinyUI(fluidPage(
  titlePanel("Concentration Calculations (M1V1 = M2V2)"),
  sidebarLayout(
    sidebarPanel(
    h1("Known Input"),
    textInput("box1", "Master Stock Concentration (mM)", value = "0"),
    textInput("box2", "Final volume (uL)", value = "0"),
    textInput("box3", "Final concentration (mM)", value = "0"),
  ),
  mainPanel(
    h3("Volume of Master Stock to be Used (uL):"),textOutput("b4"),
  )
  )
))
shinyServer(function(input, output) {

  b1 = reactive(input$box1)
  b2 = reactive(input$box2)
  b3 = reactive(input$box3)


output$b4 <- reactive({as.numeric(input$box3) * as.numeric(input$box2) / as.numeric(input$box1)

})
})
```

## ConcGadget Code
library(shiny)
library(miniUI)
shinyUI(fluidPage(
  titlePanel("Concentration Calculations (M1V1 = M2V2)"),
  sidebarLayout(
    sidebarPanel(
    h1("Known Input"),
    textInput("box1", "Master Stock Concentration (mM)", value = "0"),
    textInput("box2", "Final volume (uL)", value = "0"),
    textInput("box3", "Final concentration (mM)", value = "0"),
  ),
  mainPanel(
    h3("Volume of Master Stock to be Used (uL):"),
    textOutput("b4")))))
shinyServer(function(input, output) {
  b1 = reactive(input$box1)
  b2 = reactive(input$box2)
  b3 = reactive(input$box3)
output$b4 <- reactive({as.numeric(input$box3) * as.numeric(input$box2) / as.numeric(input$box1)})})

## Conclusions

Please note that this presentation was produced for the final project of the
Developing Data Products course. While the gadget does not work within this 
presentation file type, if you run the separate ui and server files, or app 
file, as found in my provided GitHub repository for this assignment, it works 
just fine. This was done because there are current major incompatibility issues 
with both slidify and R Presenter. This is likely because the course was written almost 10 years ago with few updates since that time.

The destination to my github repository of these files has been submitted to 
Coursera, however you can also find it here:
https://github.com/jparise858/Developing-Data-Products-Final


